Data Management for LSST Special Programs

### 2023-11-09 ap_procbounds.tex
update section title
WFD --> Main Survey

\section{Potential Processing Boundaries on Data Diversity}\label{sec:procbounds}

@@

Images which deviate significantly from the $15$ second duration for the WFD main survey 
may encounter issues in the instrument signature removal routine, in the correction for 
differential chromatic refraction, in the difference imaging analysis pipeline, and/or in 
the photometric and astrometric calibrations due to a differently sampled set of standard 
stars per CCD.

@@

However, a $2\times150$ second exposure would saturate at $r \approx 18.3$, perhaps 
leaving too few stars overlapping with e.g., templates or WFD images, for astrometric and 
photometric calibrations.

>>>>

\section{Potential Processing Boundaries}\label{sec:procbounds}

@@

Images which deviate significantly from the $15$ second duration for the Main Survey 
may encounter issues in the instrument signature removal routine, in the correction for 
differential chromatic refraction, in the difference imaging analysis pipeline, and/or in 
the photometric and astrometric calibrations due to a differently sampled set of standard 
stars per CCD.

@@

However, a $2\times150$ second exposure would saturate at $r \approx 18.3$, perhaps 
leaving too few stars overlapping with e.g., templates or Main Survey images, for astrometric and 
photometric calibrations.
